Modified replication

### 2020-06-29 rep_nosmooth/README.Rmd
add explicit replication checks
addes tables that compare both the originanl replication and our modified replication results to the values reported in Tables 1 and 2 in the paper

see #7, #8

- [variance.md](variance.md) examines how much the AUC-ROC results vary when you don't set an RNG seed. For the base specification escalation model, the variance is significantly below 0.01, and small changes in the Table 1 and 2 replications mainly occur when the distribution straddles a threshold used for rounding, e.g. 0.825. 
- `make-original-tables.R` is a by-hand coding of the values reported for Tables 1, 2, and 4 in B&S 2020.

>>>>

- [replication-check.md](replication-check.md) compares the AUC-ROC results we obtain when using smoothed ROC curves to the original B&S results (hand-copied from the paper). When taking into account the implementation fixes we made for two models, and RNG seed variation, we are able to replicate the original results/patterns. 
- [variance.md](variance.md) examines how much the AUC-ROC results vary when you don't set an RNG seed. For the base specification escalation model, the variance is significantly below 0.01, and small changes in the Table 1 and 2 replications mainly occur when the distribution straddles a threshold used for rounding, e.g. 0.825. 
- `make-original-tables.R` is a by-hand coding of the values reported for Tables 1, 2, and 4 in B&S 2020. 
- `rep-check.R` compares the results of our modified replication to the original values reported in Tables 1 and 2 of the B&S paper.
